### 2021-11-29 README.Rmd
Removed datadir. Added optimizerecdevs, started implementing hyper-stability of cpue. No EWN.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
library(aMSE)
library(TasHS)
library(rutilsMH)
library(makehtml)
library(knitr)
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- "C:/Users/User/Dropbox/A_CodeUse/aMSEUse/scenarios/"
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
datadir <- rundir
alldirExists(rundir,datadir,verbose=TRUE)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.

>>>>

* 2021-11-29 aMSE 0.0.1 Removed datadir. Started implementing hyper-stability while keeping the interface the same, so that the results from sizemod can be used.

@@

```{r example, echo=TRUE}
# a constant TAC example
starttime <- (Sys.time())
options("show.signif.stars"=FALSE,
        "stringsAsFactors"=FALSE,
        "max.print"=50000,
        "width"=240)
# declare libraries ------------------------------------------------------------
library(aMSE)
library(TasHS)
library(rutilsMH)
library(makehtml)
library(knitr)
dbdir <- getDBdir()
# Obviously you should modify the rundir and datadir to suit your own setup
prefixdir <- paste0(dbdir,"A_CodeUse/aMSEUse/scenarios/")
postfixdir <- "M15h75"
rundir <- paste0(prefixdir,postfixdir)
datadir <- rundir
alldirExists(rundir,datadir,verbose=TRUE)
controlfile <- "controlM15h75.csv"
# equilibrium zone -------------------------------------------------------------
# You now need to ensure that there is, at least, a control.csv, and a 
# constantsdata.csv file in the data directory plus some other data .csv files
# depending on how conditioned you want the model to be. Templates for the
# correct format can be produced using ctrlfiletemplate(), datafiletemplate().
# 
# Of course, usually one would use data files, control.csv and a saudata.csv, which
# is listed as the datafile within the control.csv. These must be stored in 
# rundir. There are example files in the DropBox folder:
# .\..\Dropbox\National abalone MSE\aMSE_files\scenarios\examplerun. Read the 
# 'Using_aMSE' section in the Documentation .docx file in the documentation 
# directry  Then, assuming you have the very latest version of aMSE = 500, 
# the code in the documentation file (or in the 'run_aMSE.R' file within the
# examplerun subdirectory should work.
